### 2022-11-17 paper.Rmd
Analysis updated

documentclass     : "apa6"
classoption       : "man"
#output            : papaja::apa6_pdf
output            : 
  papaja::apa6_pdf:
  latex_engine: xelatex
mainfont: Arial
---

@@

```{r apatheme, include=F}
apatheme=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica"),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        plot.title = element_text(size = 8),
        legend.text = element_text(size = 8),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

@@

@@

TIC.plot <- cowplot::plot_grid(observe.TIC.1,describe.TIC.1, awareness.TIC.1,
                                   nonjudge.TIC.1,nonreact.TIC.1,
                   labels = "AUTO",
                     align="v",
                     ncol = 3,
                     label_size = 18,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Figures/Fig6.png",TIC.plot, units = "mm", width = 174, height = 150, dpi = 600, bg = "white")

@@

reliability_plot <- cowplot::plot_grid(observe_reliability,describe_reliability, awareness_reliability,
                                   nonjudge_reliability,nonreact_reliability,
                   labels = "AUTO",
                     align="v",
                     ncol = 3,
                     label_size = 18,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")

@@

@@

@@

#Find the referent item for each factor
referents <- find_referents(esem_tareget_efa, factor_names = c("f1", "f2", "f3",
                                                               "f4", "f5"))

@@

esemComp::omega_esem(esem_fit,target_rot )

@@

#Find the referent item for each factor
referents_higher_order <- find_referents(esem_tareget_efa_higher_order , factor_names = c("f1","f2"))

@@

# rel.esm_ho <- reliability(esem_fit_higher_order , return.total = TRUE)
# 
# rel.esm_ho.m <- rel.esm_ho[4,]

@@

## Confirmatory Factor Analysis
```{r CFA-irt, include =F}

>>>>

documentclass     : "apa6"
classoption       : "man"
#output            : papaja::apa6_pdf
output            : 
  papaja::apa6_docx:
  latex_engine: xelatex
mainfont: Arial
---

@@

```{r apatheme, include=F}
apatheme=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica"),
        axis.text.x = element_text(size = 40),
        axis.text.y = element_text(size = 40),
        axis.title.x = element_text(size = 40),
        axis.title.y = element_text(size = 40),
        plot.title = element_text(size = 40),
        legend.text = element_text(size = 40),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

@@

```{r TIC-rel-plotly, include=F}
library(plotly)
ggtestinfo_se_ploty <- function(dataframe,model){
  Theta <- matrix(seq(-6,6, by = .1))
  T1 <- 0
  se <- 0
  for(i in 1:ncol(dataframe)){
    T1 <- T1 + mirt::iteminfo(extract.item(model, i), Theta)
    se <- 1/(sqrt(T1))

  data <- as.data.frame(cbind(Theta, T1, se))
  p1 <-  ggplot2::ggplot(data, ggplot2::aes(x=Theta, y=T1)) +
    ggplot2::geom_line() + ggplot2::labs(y="Test Information")+
  geom_line(data = data,linetype = "dashed",color = "red", aes(x=Theta, y=se))

  return(p1)
}

ggreliability_plotly <- function(dataframe,model){
  Theta <- matrix(seq(-6,6, by = .1))
  T1 <- 0
  se <- 0
  reliability <- 0
  for(i in 1:ncol(dataframe)){
    T1 <- T1 + mirt::iteminfo(extract.item(model, i), Theta)
    reliability <- T1/(T1+1)
  }

  data <- as.data.frame(cbind(Theta, T1,  reliability))
  p1 <-  ggplot2::ggplot(data, ggplot2::aes(x=Theta, y=reliability)) +ylim(0,1)+
    ggplot2::geom_line() + ggplot2::labs(y="rxx", x= "Theta")

  return(p1)
}

observe_tic_plotly <- plotly::ggplotly(ggtestinfo_se_ploty(observe.refit.2, observe.fit.3))
describe_tic_plotly <- plotly::ggplotly(ggtestinfo_se_ploty(describe.refit.2, describe.fit.3))
awareness_tic_plotly <- plotly::ggplotly(ggtestinfo_se_ploty(awareness.refit.2, awareness.fit.3))
nonjudge_tic_plotly <- plotly::ggplotly(ggtestinfo_se_ploty(nonjudge.refit.2, nonjudge.fit.3))
nonreact_tic_plotly <- plotly::ggplotly(ggtestinfo_se_ploty(nonreact.refit.2, nonreact.fit.3))

observe_rel_plotly <- plotly::ggplotly(ggreliability_plotly(observe.refit.2, observe.fit.3))
describe_rel_plotly <- plotly::ggplotly(ggreliability_plotly(describe.refit.2, describe.fit.3))
awareness_rel_plotly <- plotly::ggplotly(ggreliability_plotly(awareness.refit.2, awareness.fit.3))
nonjudge_rel_plotly <- plotly::ggplotly(ggreliability_plotly(nonjudge.refit.2, nonjudge.fit.3))
nonreact_rel_plotly <- plotly::ggplotly(ggreliability_plotly(nonreact.refit.2, nonreact.fit.3))

@@

TIC.plot <- cowplot::plot_grid(observe.TIC.1,describe.TIC.1, awareness.TIC.1,
                                   nonjudge.TIC.1,nonreact.TIC.1,
                   labels = "auto",
                     align="v",
                     ncol = 3,
                     label_size = 40,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Figures/Fig6.png",TIC.plot, units = "mm", width = 174, height = 150, dpi = 600, bg = "white")

@@

reliability_plot <- cowplot::plot_grid(observe_reliability,describe_reliability, awareness_reliability,
                                   nonjudge_reliability,nonreact_reliability,
                   labels = "auto",
                     align="v",
                     ncol = 3,
                     label_size = 40,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")

@@

marginal <- cbind(marginal.rel.observe,marginal.rel.describe,marginal.rel.awareness,marginal.rel.nonjudge,marginal.rel.nonreact)

@@

```{r ggscore-function}
ggscore_percentile <- function(model){
  Theta <- matrix(seq(-6,6, by = .1))
  totalscore <- (expected.test(model , Theta))
  totalscore_1 <- as.data.frame((cbind(Theta, totalscore)))

perc <- quantile(totalscore_1$totalscore,seq(from = 0,to = 1,by = 1/2))
labels <- names(perc)
m <- gregexpr('[0-9]+',labels)
labels <-regmatches(labels,m)
labels <- do.call(rbind,labels)
(labels <- paste0(round(as.numeric(paste0(labels[,1],"."))),"%"))
(perc <- round(perc,1))
(l <- paste(perc,labels,sep = "\n"))

p1 <- ggplot(totalscore_1, aes(x=Theta, y=totalscore))+geom_line()+xlab(expression(theta))+ylab(expression(T(theta)))+theme(legend.position = "none")+geom_segment(aes(x=0,xend=-Inf,y=perc[2],yend=perc[2]))+
  geom_segment(aes(x=0,xend=0,y=-Inf,yend=perc[2]))+
  geom_text(data = tibble (x = -.40, y = perc[2]+.8),
            aes(x=x, y = y,  label = perc[2]), inherit.aes = FALSE, size = 12)

# +ylab("Percentile Rank") +scale_y_continuous(breaks=perc, labels= l)+

  return(p1)
}

ggscore <- function(model){
  Theta <- matrix(seq(-6,6, by = .1))
  totalscore <- (expected.test(model , Theta))
  totalscore_1 <- as.data.frame((cbind(Theta, totalscore)))

p1 <- ggplot(totalscore_1, aes(x=Theta, y=totalscore))+geom_line()+xlab(expression(theta))+ylab(expression(T(theta)))+theme(legend.position = "none")

  return(p1)
}

ggtotalscore_tab <- function(model){
  Theta <- matrix(seq(-6,6, by = .1))
  totalscore <- (expected.test(model , Theta))
  totalscore_1 <- as.data.frame((cbind(Theta, totalscore)))

totalscore_1$totalscore <- round(totalscore_1$totalscore,0)

theta_estimatedtotalscore <- totalscore_1 %>% 
  dplyr::group_by(totalscore) %>% 
  dplyr::summarise(Theta_min= min(V1),
                   Theta_max= max(V1),
                   Theta_mean= mean(V1),
                   Theta_SD= SD(V1, na.rm=T))

  return(theta_estimatedtotalscore)
}

observe_score_percentile <- ggscore_percentile(observe.fit.3)+geom_line(color="#E64B3599")+apatheme+theme(legend.position = "none")

describe_score_percentile <- ggscore_percentile(describe.fit.3)+geom_line(color="#E64B3599")+apatheme+theme(legend.position = "none")

awareness_score_percentile <- ggscore_percentile(awareness.fit.3)+geom_line(color="#E64B3599")+apatheme+theme(legend.position = "none")

nonjudge_score_percentile <- ggscore_percentile(nonjudge.fit.3)+geom_line(color="#E64B3599")+apatheme+theme(legend.position = "none")

nonreact_score_percentile <- ggscore_percentile(nonreact.fit.3)+geom_line(color="#E64B3599")+apatheme+theme(legend.position = "none")

```{r ggscore, include=F}

observe_score <- ggscore_percentile(observe.fit.3)+geom_line(color="#E64B3599")+apatheme+theme(legend.position = "none")+geom_segment(aes(x=0,xend=-Inf,y=28.8,yend=28.8))+geom_segment(aes(x=0,xend=0,y=-Inf,yend=28.8))

describe_score <- ggscore_percentile(describe.fit.3)+apatheme+geom_line(color="#4DBBD599")+apatheme+theme(legend.position = "none")+geom_segment(aes(x=0,xend=-Inf,y=13.7,yend=13.7))+geom_segment(aes(x=0,xend=0,y=-Inf,yend=13.7))

awareness_score <- ggscore_percentile(awareness.fit.3)+apatheme+geom_line(color="#00A08799")+apatheme+theme(legend.position = "none")

nonjudge_score <- ggscore_percentile(nonjudge.fit.3)+apatheme+geom_line(color="#3C548899")+apatheme+theme(legend.position = "none")

nonreact_score <- ggscore_percentile(nonreact.fit.3)+apatheme+geom_line(color="#B09C8599")+apatheme+theme(legend.position = "none")

score.plot <- cowplot::plot_grid(observe_score ,describe_score, awareness_score,nonjudge_score,nonreact_score,

                   labels = "auto",
                     align="v",
                     ncol = 3,
                     label_size = 40,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Figures/score.png",score.plot , units = "mm", width = 174, height = 150, dpi = 600, bg = "white")

observe_score_tab <- ggtotalscore_tab(observe.fit.3)
describe_score_tab <- ggtotalscore_tab(describe.fit.3)
awareness_score_tab <- ggtotalscore_tab(awareness.fit.3)
nonjudge_score_tab <- ggtotalscore_tab(nonjudge.fit.3)
nonreact_score_tab <- ggtotalscore_tab(nonreact.fit.3)

all_score_tab <- rbind(observe_score_tab,describe_score_tab,awareness_score_tab,nonjudge_score_tab,nonreact_score_tab )
```

```{r score, results='asis'}
apa_table(all_score_tab,landscape = F, caption = "Ability vs Total Score", longtable=T)
```

@@

#Find the referent item for each factor
referents <- find_referents(esem_tareget_efa, factor_names = c("Actware", "observe", "Describe","Nonreact",                                 "Nonjudge"))

@@

@@

esem_tareget_efa_higher_order <- esem_efa(fscores,nfactors=1, fm="ml")

#Find the referent item for each factor
referents_higher_order <- find_referents(esem_tareget_efa_higher_order , factor_names = c("f1"))

@@

rel.esm_ho <- reliability(esem_fit_higher_order , return.total = TRUE)
# 
# rel.esm_ho.m <- rel.esm_ho[4,]

```{r esem-2ho, include=F}
factor_score <- psych::factor.scores(esem_data, esem_tareget_efa, method ="Thurstone")

#Find the referent item for each factor
referents_higher_order <- find_referents(esem_tareget_efa_higher_order , factor_names = c("Orientation To Experience","Self-regulated Attention"))

#  rel.esm_ho <- reliability(esem_fit_higher_order , return.total = TRUE)
# # 
# # rel.esm_ho.m <- rel.esm_ho[4,]
# Total scale omega is .74. each factors alpha f1=.54, f2 =.54. omega F1=.44, F2=.30.

@@

## Confirmatory Factor Analysis

```{r CFA-irt, include =F}
